---
title: "Desicion tree assignment"
author: "Oleksii Yehorchenkov"
date: "30 11 2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

This assignment is based on materials from [mlcourse.ai] (https://mlcourse.ai)

## Building a decision tree for predicting heart diseases

Let's read the data on heart diseases. The dataset can be downloaded from the course repo from [here](https://www.dropbox.com/s/kr1d9vsnax5wxfo/mlbootcamp5_train.csv?dl=0).

**Problem**

Predict presence or absence of cardiovascular disease (CVD) using the patient examination results.

**Data description**

There are 3 types of input features:

- *Objective*: factual information;
- *Examination*: results of medical examination;
- *Subjective*: information given by the patient.

| Feature | Variable Type | Variable      | Value Type |
|---------|--------------|---------------|------------|
| Age | Objective Feature | age | int (days) |
| Height | Objective Feature | height | int (cm) |
| Weight | Objective Feature | weight | float (kg) |
| Gender | Objective Feature | gender | categorical code |
| Systolic blood pressure | Examination Feature | ap_hi | int |
| Diastolic blood pressure | Examination Feature | ap_lo | int |
| Cholesterol | Examination Feature | cholesterol | 1: normal, 2: above normal, 3: well above normal |
| Glucose | Examination Feature | gluc | 1: normal, 2: above normal, 3: well above normal |
| Smoking | Subjective Feature | smoke | binary |
| Alcohol intake | Subjective Feature | alco | binary |
| Physical activity | Subjective Feature | active | binary |
| Presence or absence of cardiovascular disease | Target Variable | cardio | binary |

All of the dataset values were collected at the moment of medical examination.

## Task

Read the data
```{r}
> library(readr)
> mlbootcamp5_train_1_ <- read_delim("Downloads/mlbootcamp5_train.csv", ";", escape_double = FALSE, trim_ws = TRUE)
```

Transform the features: 
```{r}
#create "age in years" (`age_years`)dividing age by 365.25 and taking floor ($\lfloor{x}\rfloor$ is the largest integer that is less than or equal to $x$)
> age_years <- floor(mlbootcamp5_train_1_$age/365.25)
> head(age_years)
#remove "age" feature
> mlbootcamp5_train_1_[ , !(names(mlbootcamp5_train_1_) %in% c("age"))]
#transfrom `cholesterol` and `gluc` to factor
> mlbootcamp5_train_1_$cholesterol <- as.factor(mlbootcamp5_train_1_$cholesterol)
> mlbootcamp5_train_1_$gluc <- as.factor(mlbootcamp5_train_1_$gluc)
```

Split data into train and test parts in the proportion of 7/3.
The target feature is `cardio`

```{r}
> install.packages('caret')
> library(caret)
> index <- createDataPartition(mlbootcamp5_train_1_$cardio, p = 0.7, list = FALSE)
> train <- mlbootcamp5_train_1_[index, ]
> test <- mlbootcamp5_train_1_[-index,]
```

Train a decision tree on the dataset `training` with **max depth equal to 3**. For setting this parameter use function `rpart::rpart.control`. Use default cross calidation parameters.

```{r}
> install.packages('rpart')
> library(rpart)
> training <- train(cardio~ ., data = train, method = "rpart", control = rpart.control(maxdepth = 3))
# Your code here
```

Plot final tree with `rattle` library

```{r}
> install.packages('RGtk2')
> install.packages("rattle", dependencies = TRUE)
> fancyRpartPlot(training)
```

What is the accuracy of prediction on test data?

```{r}
pred <- predict(training, test)
> x <- as.integer(pred)
> y <- test$cardio
> l <- union(x, y)
> t <- table(factor(x, l), factor(y, l))
accuracy <- confusionMatrix(t)
```
Now set cross validation parameters: `method = "cv"`, `number = 5`. Tree parameters set to default.
> trControl <- trainControl(method = "cv", number = 5)
> training <- train(cardio ~ ., data = train, method = "rpart", trControl = trControl)
```{r}
# Your code here
```

Plot final tree with `rattle` library

```{r}
# Your code here
> fancyRpartPlot(training)
```

What is the accuracy of prediction on test data?

```{r}
> pred <- predict(training, test)
> x <- as.integer(pred)
> y <- test$cardio
> l <- union(x, y)
> t <- table(factor(x, l), factor(y, l))
confusionMatrix(t)
```
Does the accuracy became better or not?

#accuracy_1: 0.5008, accuracy_2: 0.5008. So the accuracy didn't seem to change.
